%!TEX root = ../thesis.tex
% ******************************* Thesis Appendix A ****************************
\definecolor{mGreen}{rgb}{0,0.6,0}
\definecolor{mGray}{rgb}{0.5,0.5,0.5}
\definecolor{mPurple}{rgb}{0.58,0,0.82}
\definecolor{backgroundColour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{CStyle}{
	backgroundcolor=\color{backgroundColour},   
	commentstyle=\color{mGreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{mGray},
	stringstyle=\color{mPurple},
	basicstyle=\footnotesize,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	numbers=left,                    
	numbersep=5pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=2,
	language=C
}


\lstdefinestyle{CMakeStyle}{
	backgroundcolor=\color{backgroundColour},   
	basicstyle=\footnotesize,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	numbers=left,                    
	numbersep=5pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=2,
}


\chapter{Percolation} 
\section{Algorithm}
\section{Code}
	
	Each header file starts with a directive \textit{\#ifndef} and \textit{\#define}, which is necessary because one header file is needed multiple times and including it more than once results in error. These directive prevents it. Of course this directive must be closed by \textit{\#endif}.
	
	
	\subsection{Index}
	Here the notion of index of site and index of bond is defined. Site index has two element which determine row and column. Bond Index had three element describing bond type, row, column. Bond type can be horizontal or vertical.
	\input{Appendix1/codes/index}	
	
	
	\subsection{Site}
	The site class contains all information about a site, e.g., if it is active or not and if it is then what is it's group id or relative index.
	\input{Appendix1/codes/site}
	
	\subsection{Bond}
	The bond class contains all information about a bond, e.g., if it is active or not and if it is then what is it's group id.
	\input{Appendix1/codes/bond}
			
	\subsection{Lattice}
	The lattice class consists of array of sites and bonds. This class contains information about lattice size. And contains functions to view the lattice differently in the console.
	\input{Appendix1/codes/lattice}
	
	\subsection{Exception}
	Different types of exceptions.
	\input{Appendix1/codes/exception}
	
	\subsection{Cluster}
	The cluster class contains all information about a cluster. Number of sites and bonds in a cluster and the id of the cluster is contained in a cluster.
	\input{Appendix1/codes/cluster}
	
	\subsection{Percolation}
	\input{Appendix1/codes/percolation}
	\input{Appendix1/codes/site-percolation}
	
	\subsection{Utilities}
	\input{Appendix1/codes/printer}
	\input{"Appendix1/codes/time_tracking"}
	\input{Appendix1/codes/type}
	
	\subsection{Test}
	\input{Appendix1/codes/test}
	
	\subsection{Main}
	The main function receives 3 additional command line argument. First one is an integer $l\in{0,1,2}$ which determine the range of interaction. Second one is the length of the lattice. And third one is the size of the ensemble. For example, $1 200 5000$ will run the program for $l=1$, $L=200$ for ensemble size of $5000$
	\input{Appendix1/codes/main}
	
	\subsection{CMakeLists}
	\input{Appendix1/codes/cmakelists}
	
	\subsection{complete code}
	Complete code for RSBD model on square lattice is available at
	\url{https://github.com/sha314/SqLattice_RSBD}
	or use the git link to clone the repository
	\url{https://github.com/sha314/SqLattice_RSBD.git}
	\\
	Detailed version of the same program with other extensions are available at
	\url{https://github.com/sha314/SqLatticePercolation}
	or the git link
	\url{https://github.com/sha314/SqLatticePercolation.git}



